\chapter{Conclusion}\label{chapter:conclusion}

In conclusion, the idea of an index token is a implementable idea with the system prototype for the DFAM token demonstrate in earlier sections. The prototype has proved the basic functionalities of an index fund with the DFAM index token holding the underlying assets. Through purchasing the DFAM token, investors can prove their owner of the underlying components and can also redeem their capitals at anytime by selling the DFAM tokens back to the decentralized index fund. With the backing Uniswap's contract ecosystem, the index fund in our prototype has shown that both investment and redemption are functional on the Ropsten testnet. Regarding the governance functionalities, our decentralize index fund has also proved that portfolio update and portfolio rebalancing are also functional with grace period for the execution of these functionalities. Token portfolio can be updated by tokens of a pre-defined category, with classified token data can be automatically retrieved from the ITSA database for the portfolio selection process. In summary, all the required functionalities of an index fund are functional in the decentralized environment and are ensured by unit tests and the deployments on the Ropsten network.

However, the system is still not fully decentralized with the presence of centralized oracle node and the ITSA database. Both of these components are required for the update portfolio process and therefore, are relevant for the validity of the component tokens in the portfolio. We have suggested a possible approach through voting and incentive mechanism to address the centralization issue of ITSA data with some caveats and also the mitigation of the centralization of the oracle node with the multisig mechanism. Nonetheless, the index fund is still not actually practical due to the swapping fees of Uniswap. Therefore, further investigation on the economical and financial perspectives should also be performed before a public deployment of the DeFi index fund on the Ethereum Mainnet.